### 2018-08-07 paper/sphinxes.tex
sphinxes: reinstated packet, some grammar edits

\begin{figure}
  \includegraphics[width=\linewidth]{figures/OR-POR.png}
  \caption{\label{fig:OR-POR}%
    Illustration of the conceptual difference between traditional onion routing 
    and mixing (top) and \ac{SPOR} (bottom).
    %\commentDaniel{This figure should be fixed, issue \#42.}
  }
\end{figure}

@@

If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
If \(t\) is already in the table of seen messages, drop the message.
Otherwise, add \(t\) to the table and decrypt \(\beta\):
\begin{equation*}
  L'\concat C'\concat \gamma'\concat \beta'\gets \{\beta\concat 0_{w_H 
    \kappa}\}
  \oplus \prg(\hash_\prg(s_i))
\end{equation*}

@@

Otherwise. \(\beta'\) should be forwarded to \(L'\).
Compute the blinding factor \(b\gets \hash_\blind(\alpha, s_i)\) and let 
\(\alpha'\gets \alpha^b\).
Choose a node \(n\rgets L'\) uniformly at random.
Send \((\alpha', C', \beta', \gamma')\) to \(n\).
If sending to \(n\) fails, choose another node from \(L'\) uniformly at random.
If all nodes in \(L'\) fails, the algorithm drops the packet and silently 
fails.

>>>>

\begin{figure}
  \centering
  %  \includegraphics[width=\linewidth]{figures/OR-POR.png}
    \includegraphics[width=0.65\linewidth]{figures/principle_SPOR.pdf}
  \caption{\label{fig:OR-POR}%
    Illustration of the conceptual difference between traditional onion routing

    and mixing (OR, top) and \ac{SPOR} (bottom).

    %\commentDaniel{This figure should be fixed, issue \#42.}
  }
\end{figure}

@@

If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
If \(t\) is already in the table of seen packets, drop the packet.
Otherwise, add \(t\) to the table and decrypt \(\beta\):
\begin{equation*}
  L'\concat C'\concat \gamma'\concat \beta'\gets \{\beta\concat 0_{w_H 
    \kappa}\}
  \oplus \prg(\hash_\prg(s_i))
\end{equation*}

@@

Otherwise. \(\beta'\) should be forwarded to \(L'\).
Compute the blinding factor \(b\gets \hash_\blind(\alpha, s_i)\) and let 
\(\alpha'\gets \alpha^b\).
Choose a node \(n\rgets L'\) uniformly at random.
Send \((\alpha', C', \beta', \gamma')\) to \(n\).
If sending to \(n\) fails, choose another node from \(L'\) uniformly at random.
If all nodes in \(L'\) fail, the algorithm drops the packet and fails silently.
